Methods for Large Scale Learning to Rank

### 2014-04-04 report/Chapters/CrossBenchmarkComparison.tex
described en evaluated kolommen gesplitst

\section{Evaluation Results Found in Literature}
\begin{tabular}{llll}
AdaRank-\ac{MAP} & FenchelRank & LambdaRank & RankDE \\ 
AdaRank-\ac{nDCG} & FocusedBoost & LARF & Ranking Committee Perceptron \\ 
ADMM & FocusedNet & ListMLE & RankMGP \\ 
Approx\ac{AP} & FocusedSVM & ListNet & RankNet \\ 
Approx\ac{nDCG} & FPRank & ListReg & RankRLS \\ 
BagBoo & FRank & LRUF & RankSVM \\ 
Best Single Feature & FSMRank & MBP & RankSVM-Primal \\ 
BL-MART & FSM$^{MAP}$ & MHR & RankSVM-Struct \\ 
BoltzRank-Single & GAS-E & MultiStageBoost & RE-QR \\ 
BoltzRank-Pair & GPRank & NewLoss & REG-SHF-SDCG \\ 
BT & GRankRLS & OWPC & Regression \\ 
C-CRF & GroupCE & RankELM (pointwise) & RSRank \\ 
CA & GroupMLE & RankELM (pairwise) & SmoothGrad \\ 
 &  & TM & VFLR \\ 
CCRank & IntervalRank & PERF-MAP & SmoothRank \\ 
CoList & KeepRank & PermuRank & SoftRank \\ 
Consistent-RankCosine & Kernel-PCA & Q.D.KNN & SortNet \\ 
CRR & KL-CRF & RandomForest & SparseRank \\ 
DCMP & Regression with L2-regularisation & Rank-PMBGP & SVD-RankBoost \\ 
DirectRank & LAC-MR-OR & RankAgg\ac{nDCG} & SVM$^{MAP}$ \\ 
Energy\ac{nDCG} & LambdaMART & RankBoost & SwarmRank \\ 
FBPCRank & LambdaNeuralRank & RankCSA & TGRank \\ 
\end{tabular}

>>>>

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\scalebox{0.85}{
\begin{tabular}{|l|l|l||l|l|l|}
Method & Described & Evaluated & Method & Described & Evaluated \\ 
AdaRank-\acs{MAP} &  &  & Linear Regression &  &  \\ 
AdaRank-\acs{nDCG} &  &  & List\acs{MLE} &  &  \\ 
ADMM &  &  & ListNet &  &  \\ 
Approx\acs{AP} & \cite{Qin2010b} & \cite{Qin2010b} & ListReg & \cite{Wu2011} & \cite{Wu2011} \\ 
Approx\acs{nDCG} & \cite{Qin2010b} & \cite{Qin2010b} & LRUF & \cite{Torkestani2012b} & \cite{Torkestani2012b} \\ 
BagBoo &  &  & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 
Best Single Feature &  &  & MHR &  &  \\ 
BL-MART & \cite{Ganjisaffar2011c} & \cite{Ganjisaffar2011c} & MultiStageBoost & \cite{Kao2013} & \cite{Kao2013} \\ 
BoltzRank-Single & \cite{Volkovs2009} & \cite{Volkovs2009} & NewLoss & \cite{Peng2010} & \cite{Peng2010} \\ 
BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009} & OWPC & \cite{Usunier2009} & \cite{Usunier2009} \\ 
BT & \cite{Zhou2008} & \cite{Zhou2008} & PERF-\acs{MAP} &  &  \\ 
C-\acs{CRF} & \cite{Qin2008b} & \cite{Qin2008b} & PermuRank & \cite{Xu2008} & \cite{Xu2008} \\ 
CA &  &  & Q.D.\acs{KNN} &  &  \\ 
CCRank &  &  & RandomForest & \cite{Gomes2013} & \cite{Gomes2013} \\ 
CoList &  &  & Rank-PMBGP &  &  \\ 
Consistent-RankCosine &  &  & RankAgg\acs{nDCG} &  &  \\ 
DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost &  &  \\ 
DirectRank & \cite{Tan2013} & \cite{Tan2013} & RankCSA & \cite{He2010} & \cite{He2010} \\ 
Energy\acs{nDCG} & \cite{Freno2011} & \cite{Freno2011} & RankDE &  &  \\ 
FBPCRank & \cite{Lai2011} & \cite{Lai2011} & RankELM (pairwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FenchelRank & \cite{Lai2013} & \cite{Lai2013} & RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FocusedBoost & \cite{Niu2012} & \cite{Niu2012} & Ranking Committee Perceptron & \cite{Elsas2008} & \cite{Elsas2008} \\ 
FocusedNet & \cite{Niu2012} & \cite{Niu2012} & RankMGP &  &  \\ 
Focused\acs{SVM} & \cite{Niu2012} & \cite{Niu2012} & RankNet &  &  \\ 
FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{RLS} &  &  \\ 
FRank &  &  & Rank\acs{SVM} &  &  \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c} & Rank\acs{SVM}-Primal &  &  \\ 
FSM$^{\acs{MAP}}$ &  &  & Rank\acs{SVM}-Struct &  &  \\ 
GAS-E &  &  & RE-QR & \cite{Veloso2010} & \cite{Veloso2010} \\ 
\acs{GP}Rank &  &  & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 
GRank\acs{RLS} & \cite{Pahikkala2010} & \cite{Pahikkala2010} & Ridge Regression &  &  \\ 
Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank &  &  \\ 
Group\acs{MLE} &  &  & SmoothGrad &  &  \\ 
IntervalRank & \cite{Moon2010} & \cite{Moon2010} & SmoothRank & \cite{Chapelle2010} & \cite{Chapelle2010} \\ 
\acs{IP}Rank &  &  & SoftRank &  &  \\ 
KeepRank & \cite{Chen2009} & \cite{Chen2009} & SoftNet & \cite{Rigutini2008} & \cite{Rigutini2008} \\ 
Kernel-\acs{PCA} &  &  & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
KL-\acs{CRF} &  &  & \acs{SVD}-RankBoost & \cite{Lin2009} & \cite{Lin2009} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ &  &  \\ 
LambdaMART &  &  & SwarmRank &  &  \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank &  &  \\ 
LambdaRank &  &  & TM & \cite{Zhou2008} & \cite{Zhou2008} \\ 
LARF & \cite{Torkestani2012} & \cite{Torkestani2012} & VFLR &  &  \\ 
\end{tabular}}
\caption{Learning-to-Rank algorithms with measurements on benchmark datasets}
\label{ltr_methods_used}
\end{table}
